---
title: "R Notebook"
author: "Rich Chu, Matt Lawson"
output: html_notebook
---

# Lab 7: Five Scores and Several Months Ago

## Part I: Import and Look

### Problem 1

```{r}
quiz <- as.data.frame(read.csv("quiz.csv"))
class(quiz)
```

### Problem 2

```{r}
plot(quiz)
```
The students' scores across all quizzes do not appear to be associated because each scores are truely random

## Part II: Every Quiz Is Exactly the Same?

### Problem 3
```{r}
plot(quiz$Q2,quiz$Q6,xlab= "Quiz 2", ylab= "Quiz 6")
```



### Problem 4

```{r}
cor(quiz$Q2,quiz$Q6)
```
Yes there is a positive association between the quiz percentages because the value is positive

### Problem 5

```{r}
bootstrap.cor <- function(x,y,B= 2000){
  data.x <- data.frame(x)
  data.y <- data.frame(y)
  boot.est <- vector(length= B)
  for(i in 1:B){
    boot.x <- data.x[sample(1:nrow(data.x),replace=TRUE),]
    boot.y <- data.y[sample(1:nrow(data.y),replace=TRUE),]
    boot.est[i] <- cor(boot.x,boot.y)
  }
  return(boot.est)
}
```

### Problem 6

```{r}
boot <- bootstrap.cor(quiz$Q2,quiz$Q6,B= 5000)
hist(boot)
```
The bootstrap data from the correlation between quiz 2 and quiz 6 appear to be normally distributed around 0

### Problem 7

```{r}
quantile(boot,c(0.025,0.975))
cor.test(quiz$Q2,quiz$Q6)$conf.int[1:2]
```
The bootstrap interval has a larger range of values than the normal interval. The lower bootstrap interval is also negative while the normal interal is positive. We can reject the null hypothesis and conclude that there is an association between the Quiz 2 and Quiz 6 scores. The significance level is 0.05.

## Part III: The "It" Factor

### Problem 8

```{r}
cov.mat <- cov(quiz)

cov(x = quiz$Q2, y = quiz$Q3)
cov.mat[1,2]
```

These are the same.

### Problem 9

```{r}

eigen.vals <- eigen(cov.mat)$value 
eigen.vals
```

It's sorted greatest to least.

### Problem 10

```{r}
sum(eigen.vals)
sum(diag(cov.mat))
```

These are the same.

### Problem 11

```{r}
eigen.vals[1]/sum(eigen.vals)
```

64.2% of the variance is captured by the first principal component analysis.

### Problem 12

```{r}
bootstrap.eigenratio <- function(mat, B = 2000){
?eigen
  
  boot.est <- vector(length= B)
  for(i in 1:B){
    
    boot.est[i] <- mat[sample(1:nrow(mat),replace=TRUE),]
  }
  cov.mat <- cov(boot.est)
  eigen.vals <- eigen(x=cov.mat)$value
  eigen.ratio <- eigen.vals[1]/sum(eigen.vals)
  return(eigen.ratio)
}
```


### Problem 13

```{r}
bootstrap.eigenratio(quiz)
```

