---
title: "R Notebook"
author: "Rich Chu, Matt Lawson"
output: html_notebook
---

# Lab 7: Five Scores and Several Months Ago

## Part I: Import and Look

### Problem 1

```{r}
quiz <- as.data.frame(read.csv("quiz.csv"))
```

### Problem 2

```{r}
plot(quiz)
```
The students' scores across all quizzes do not appear to be associated because each scores are truely random

## Part II: Every Quiz Is Exactly the Same?

### Problem 3
```{r}
plot(quiz$Q2,quiz$Q6,xlab= "Quiz 2", ylab= "Quiz 6")
```



### Problem 4

```{r}
cor(quiz$Q2,quiz$Q6)
```
Yes there is a positive association between the quiz percentages because the value is positive

### Problem 5

```{r}
bootstrap.cor <- function(x,y,B= 2000){
  data.x <- data.frame(x)
  data.y <- data.frame(y)
  boot.est <- vector(length= B)
  for(i in 1:B){
    boot.x <- data.x[sample(1:nrow(data.x),replace=TRUE),]
    boot.y <- data.y[sample(1:nrow(data.y),replace=TRUE),]
    boot.est[i] <- cor(boot.x,boot.y)
  }
  return(boot.est)
}
```

### Problem 6

```{r}
boot <- bootstrap.cor(quiz$Q2,quiz$Q6,B= 5000)
hist(boot)
```
The bootstrap data from the correlation between quiz 2 and quiz 6 appear to be normally distributed around 0

### Problem 7

```{r}
quantile(boot,c(0.025,0.975))
cor.test(quiz$Q2,quiz$Q6)$conf.int[1:2]
```
The bootstrap interval has a larger range of values than the normal interval. The lower bootstrap interval is also negative while the normal interal is positive

## Part III: The "It" Factor




